---
title: "MDML_Fianl_Project_YJ_FT_OC"
output: html_notebook
---
Filter 
  scaffolding problems
  open text problems

creating historical variables

# problems solved (lower order ids)
%/# correct (correct n lower order ids)
Average # hints per problem that has hints
% of problem in which student requested hints when hints are available
Average # scaffolding
Average time of first response
% bottom out out of questions with hints
Average historical attempt count

i. Predicting students' using hints/scaffolding -- all data
ii. Predict student bottom out behavior -- all data
iii. Predict correct incorrect -- no hints/scaffolding

For each we choose between 2 models (logistic regression and random forest)
  auc
  
feature selection - forward stepwise selection


```{r}
library(tidyverse)
```


```{r}
#Pulling data
rawdata <- read.csv("skill_builder_data.csv")

#Only consider main problem (main problem=1, scaffolding problem=0)
rawdata <- rawdata %>% filter(original==1)

#Use the latest order id as reference
last_rawdata <- rawdata %>% group_by(user_id) %>% arrange(order_id) %>% slice(n())

historical <- merge(last_rawdata, rawdata[c('user_id', 'order_id', 'problem_id', 'correct', 'hint_count', 'hint_total', 'bottom_hint', 'ms_first_response', 'attempt_count')], by = 'user_id', all.x = TRUE, allow.cartesian=TRUE)

historical <- historical %>% filter(order_id.y < order_id.x) %>% distinct

historical <- historical %>% group_by(user_id, order_id.x) %>% 
  summarise(total_problem_solved = sum(correct.y),
            num_problem = length(unique(problem_id.y)),
            percent_problem_solved=total_problem_solved/num_problem,
            questions_with_hints = sum(hint_total.y>0),
            total_hints = sum(hint_total.y),
            avg_hints_per_problem = total_hints/questions_with_hints,
            problem_requested_hint = sum(hint_count.y>0),
            percent_question_requested_hint = problem_requested_hint/num_problem,
            avg_response_time = mean(ms_first_response.y),
            total_bottom_hint = sum(bottom_hint.y == 1),
            percent_bottom_out = total_bottom_hint/questions_with_hints,
            avg_attempt_count = mean(attempt_count.y)) 


```
